Spatial Reasoning and Statistical Graphics

### 2014-10-13 Paper/Draft1/TestingVisualAptitude.Rnw
Define k a bit earlier and also add the standard deviation.

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. 
Scoring of all test results was done such that random guessing leads to an expected value of 0; therefore each question answered correctly contributes to the score by 1, while a wrong answer is scored by $-1/(k-1)$. Thus, for a test consisting of multiple choice questions with $k$ suggested answers with a single correct answer each, the score is calculated as
\begin{eqnarray}\label{eq.scoring}
\# \text{correct answers } - 1/(k-1) \cdot \# \text{wrong answers}.
\end{eqnarray}
This allows us to compare each participant's score in light of how many problems were attempted as well as the number of correct responses. Combining accuracy and speed into a single number does not only make a comparison of test scores easier,  this scoring mechanism is also used on many standardized tests, such as the SAT and the battery of psychological tests \citep{diamond1973correction, ekstrom1976manual} which parts of this test are drawn from.

@@

\begin{eqnarray*}
\text{Var}(X_{n, k}) &=& n^2 \text{Var}(X_{1, k}) = \\
&=& n^2 (\underbrace{1/k \cdot 1^2}_{\text{correct answer}}+ \underbrace{(-1/(k-1))^2 \cdot (k-1)/k}_{\text{wrong answer}}) = \\
&=& n^2/(k-1).
\end{eqnarray*}

\newtext{The above consideration only assumes independence between questions, which is granted. While we only consider a test consisting of questions with the same number of choices, $k$, an extension to varied number of answers is trivial and has been done in the adjustment for the figure classification score.}

>>>>

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. 
Scoring of all test results was done such that random guessing leads to an expected value of 0; therefore each question answered correctly contributes to the score by 1, while a wrong answer is scored by $-1/(k-1)$, where $k$ is the total number of possible answers to the question. Thus, for a test consisting of multiple choice questions with $k$ suggested answers with a single correct answer each, the score is calculated as
\begin{eqnarray}\label{eq.scoring}
\# \text{correct answers } - 1/(k-1) \cdot \# \text{wrong answers}.
\end{eqnarray}
This allows us to compare each participant's score in light of how many problems were attempted as well as the number of correct responses. Combining accuracy and speed into a single number does not only make a comparison of test scores easier,  this scoring mechanism is also used on many standardized tests, such as the SAT and the battery of psychological tests \citep{diamond1973correction, ekstrom1976manual} which parts of this test are drawn from.

@@

\begin{eqnarray*}
\text{Var}(X_{n, k}) &=& n^2 \text{Var}(X_{1, k}) = \\
&=& n^2 (\underbrace{1/k \cdot 1^2}_{\text{correct answer}}+ \underbrace{(-1/(k-1))^2 \cdot (k-1)/k}_{\text{wrong answer}}) = \\
&=& n^2/(k-1).\\
\text{Sd}(X_{n, k}) &=& n/sqrt{k-1}
\end{eqnarray*}

\newtext{The above consideration only assumes independence between questions, which is granted. While we only consider a test consisting of questions with the same number of choices, $k$, an extension to varied number of answers is trivial and has been done in the adjustment for the figure classification score.}
\newtext{In order to ensure all tests have similar variance, we scaled test scores by the standard deviation under random guessing. This approach also allows us to compare the test scores using similar orders of magnitude.}
